---
title: "ML_assignment"
author: "Siva Prakaash S M"
date: "29/07/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# install.packages('caret');
# install.packages('xgboost');
# install.packages("naivebayes")
# install.packages('tidyverse')

```
Including neccessary libraries.
```{r}
library(dummies)
library(caTools)
library(caret)
library(xgboost)
library(mlbench)
library(class)
library(naivebayes)
library(tidyverse)
```

## Loading the data.
```{r cars}
data = read.csv('Cars.csv')

```

## Removing null value as there were one row.
```{r}
data  = data[complete.cases(data),]
```


## Mulitnominal to binominal class 0 for cars and 1 for 2 wheeler and pubic transport(others).
## converting the gender column to 1(Male) and 0(Female).

```{r}
# Updating the Target varaible to binominal class
levels(data$Transport)
levels(data$Transport) <- list("0"="Car", "1"="2Wheeler", "1"="Public Transport")
str(data)
levels(data$Gender) <- list("1"="Male", "0"="Female")
data$Gender = as.numeric(as.character(data$Gender))
nrow(data)
```

```{r}
# Normalize Data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x))) 
}

normalizeData <- as.data.frame(lapply(data[0:8], normalize))
normalizeData$Transport = data$Transport

```

```{r}
head(data)
tail(data)
```
## Test Train split (70-30)
```{r}
set.seed(100)
split = sample.split(normalizeData$Transport, SplitRatio = 0.7)
traindata = subset(normalizeData, split == TRUE)
testdata = subset(normalizeData, split == FALSE)
prop.table(table(traindata$Transport))
prop.table(table(testdata$Transport))

data_train_labels <- traindata$Transport
data_test_labels <- testdata$Transport

```
```{r}
#ssTrain = traindata[,c(7)]
#head(traindata[,c(8)])

#Dependent Variables
data_train_labels <- traindata$Transport
data_test_labels <- testdata$Transport

```


```{r}
#IV variables
knn_traindata = traindata[,c(1:8)]
knn_testdata = testdata[,c(1:8)]

logittestdata = testdata;
testdata = testdata[,c(1:8)]

```

#Knn Model
```{r}
# Training the model
data_test_pred <- knn(train = knn_traindata, test = knn_testdata, cl = data_train_labels, k=3)
```

```{r}
confusionMatrix(data_test_pred,
                data_test_labels, 
                positive = "0",
                mode="everything")
```
## Naivebayes

```{r}
nb <- naive_bayes(Transport ~ ., traindata)
data_pred <- predict(nb,testdata,type="class")
confusionMatrix(data_pred,  data_test_labels, positive = "0", mode="everything")
```

## Logit
```{r}
logitTrain = glm(Transport ~ ., data = traindata[, -c(2,3,4)], family=binomial)
summary(logitTrain)
Trainprediction <- predict(logitTrain, type = "response")
nrow(traindata)
length(Trainprediction)

Testprediction <- predict(logitTrain, newdata=logittestdata[, -c(2,3,4)], type = "response")

Testcutoff = floor(Testprediction+0.20)

Testconfmat = table(Predicted=Testcutoff, Actual=data_test_labels)
confusionMatrix(Testconfmat, positive="0", mode="everything")

```
## xgboost
```{r}
xgboostModel <- train(
  Transport ~., data = traindata, method = "xgbTree",
  trControl = trainControl("cv", number = 3)
)
```

```{r}
# Best tuning parameter
xgboostModel$bestTune
varImp(xgboostModel)
plot(varImp(xgboostModel))
```

```{r}
# Make predictions on the test data
predicted.classes <- xgboostModel %>% predict(testdata)
head(predicted.classes)
```

```{r}
TestconfmaXg= table(Predicted=predicted.classes, Actual=data_test_labels)
confusionMatrix(TestconfmaXg, positive="0", mode="everything")
```
# Caret package logit. (No tunning parameter available) [Ignore this, just for practice]
```{r}
lmModel <- train(
  Transport ~., data = traindata, method = "glm",
  trControl = trainControl("cv", number = 3)
)
predictedLmData <- lmModel %>% predict(testdata)
Testlmdata= table(Predicted=predictedLmData, Actual=data_test_labels)
confusionMatrix(Testlmdata, positive="0", mode="everything")
```
## knn with caret train package - [Ignore this, just for practice]
```{r}
knnFit1 <- train(knn_traindata, data_train_labels,
method = "knn",
tuneLength = 10,
trControl = trainControl(method = "cv", number = 3))

predictedknnData <- knnFit1 %>% predict(knn_testdata)

Testknndata= table(Predicted=predictedknnData, Actual=data_test_labels)
confusionMatrix(Testknndata, positive="0", mode="everything")
```